---
title: "Quantifying_casestudy4"
author: "Brandon"
date: "September 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#URL for MEN and Library

library(XML)

library(tidyverse)


ubase = "http://www.cherryblossom.org/"



#### Revised URLS
menURLsV2 = 
  c("results/1999/cb99m.html", #"cb99m.htm"
    "results/2000/Cb003m.htm", #"cb003m.htm"
    "results/2001/oof_m.html", #"results/2001/oof_m.html"
    "results/2002/oofm.htm", #"results/2002/oofm.htm"
    "results/2003/CB03-M.HTM", #"results/2003/CB03-M.HTM"
    "results/2004/men.htm", #"results/2004/men.htm"
    "results/2005/CB05-M.htm", #"results/2005/CB05-M.htm"
    "results/2006/men.htm", #"results/2006/men.htm"
    "results/2007/men.htm", #"results/2007/men.htm"
    "results/2008/men.htm", #"results/2008/men.htm"
    "results/2009/09cucb-M.htm", #"results/2009/09cucb-M.htm"
    "results/2010/2010cucb10m-m.htm", #"results/2010/2010cucb10m-m.htm"
    "results/2011/2011cucb10m-m.htm", #"results/2011/2011cucb10m-m.htm"
    "results/2012/2012cucb10m-m.htm" #"results/2012/2012cucb10m-m.htm"
    )
####



#### Revised URLS
urlsV2 = paste(ubase, menURLsV2, sep="")
urlsV2[1:4]

```

```{r}

#FUNCTIONS

#extractResTablev2

extractResTableV2 =
  #
  # Retrieve data from web site, 
  # find the preformatted text,
  # and write lines or return as a character vector.
  #
  function(url = "http://www.cherryblossom.org/results/2009/09cucb-F.htm",
           year = 1999, sex = "male", file = NULL)
  {
    #added encoding for windows users who get an "A" symbol
    doc = htmlParse(url, encoding="UTF-8")
    
    if (year == 2000) {
      # Get preformatted text from 4th font element
      # The top file is ill formed so the <pre> search doesn't work.
      ff = getNodeSet(doc, "//font")
      txt = xmlValue(ff[[4]])
      els = strsplit(txt, "\r\n")[[1]]
    }
    else if (year == 2009 & sex == "male") { 
      # Get preformatted text from <div class="Section1"> element
      # Each line of results is in a <pre> element
      div1 = getNodeSet(doc, "//div[@class='Section1']")
      pres = getNodeSet(div1[[1]], "//pre")
      els = sapply(pres, xmlValue)
    }
    else if (year == 1999 & sex == "male") { # have to add this else if statement
      # Get preformatted text from <pre> elements
      pres = getNodeSet(doc, "//pre")
      txt = xmlValue(pres[[1]])
      els = strsplit(txt, "\n")[[1]]   
    } 
    else {
      # Get preformatted text from <pre> elements
      pres = getNodeSet(doc, "//pre")
      txt = xmlValue(pres[[1]])
      els = strsplit(txt, "\r\n")[[1]]   
    } 
    
    if (is.null(file)) return(els)
    # Write the lines as a text file.
    writeLines(els, con = file)
  }

extractResTableV3 =
  #
  # Retrieve data from web site, 
  # find the preformatted text,
  # and write lines or return as a character vector.
  #
  function(url = "http://www.cherryblossom.org/results/2009/09cucb-F.htm",
           year = 1999, sex = "female", file = NULL)
  {
    #added encoding for windows users who get an "A" symbol
    doc = htmlParse(url, encoding="UTF-8")
    
    if (year == 2000) {
      # Get preformatted text from 4th font element
      # The top file is ill formed so the <pre> search doesn't work.
      ff = getNodeSet(doc, "//font")
      txt = xmlValue(ff[[4]])
      els = strsplit(txt, "\r\n")[[1]]
    }
    #else if (year == 2009 & sex == "female") {
      # Get preformatted text from <div class="Section1"> element
      # Each line of results is in a <pre> element
      #div1 = getNodeSet(doc, "//div[@class='Section1']")
      #pres = getNodeSet(div1[[1]], "//pre")
      #els = sapply(pres, xmlValue)
    #}
    else if (year == 1999 & sex == "female") { # have to add this else if statement
      # Get preformatted text from <pre> elements
      pres = getNodeSet(doc, "//pre")
      txt = xmlValue(pres[[1]])
      els = strsplit(txt, "\n")[[1]]   
    } 
    else {
      # Get preformatted text from <pre> elements
      pres = getNodeSet(doc, "//pre")
      txt = xmlValue(pres[[1]])
      els = strsplit(txt, "\r\n")[[1]]   
    } 
    
    if (is.null(file)) return(els)
    # Write the lines as a text file.
    writeLines(els, con = file)
  }


#findColLocs

findColLocs = function(spacerRow) {

  spaceLocs = gregexpr(" ", spacerRow)[[1]]
  rowLength = nchar(spacerRow)

  if (substring(spacerRow, rowLength, rowLength) != " ")
    return( c(0, spaceLocs, rowLength + 1))
  else return(c(0, spaceLocs))
}

selectCols = function(shortColNames, headerRow, searchLocs) {
  sapply(shortColNames, function(shortName, headerRow, searchLocs){
    startPos = regexpr(shortName, headerRow)[[1]]
    if (startPos == -1) return( c(NA, NA) )
    index = sum(startPos >= searchLocs)
    c(searchLocs[index] + 1, searchLocs[index + 1])
  }, headerRow = headerRow, searchLocs = searchLocs )
}


#extractVariables

extractVariables = 
function(file, varNames =c("name", "home", "ag", "gun",
                           "net", "time"))
{
  
  # Find the index of the row with =s
  eqIndex = grep("^===", file)
  # Extract the two key rows and the data 
  spacerRow = file[eqIndex] 
  headerRow = tolower(file[ eqIndex - 1 ])
  body = file[ -(1 : eqIndex) ]
       # Remove footnotes and blank rows
  footnotes = grep("^[[:blank:]]*(\\*|\\#)", body)
  if ( length(footnotes) > 0 ) body = body[ -footnotes ]
  blanks = grep("^[[:blank:]]*$", body)
  if (length(blanks) > 0 ) body = body[ -blanks ]
  
  
  # Obtain the starting and ending positions of variables   
  searchLocs = findColLocs(spacerRow)
  locCols = selectCols(varNames, headerRow, searchLocs)
  
  Values = mapply(substr, list(body), start = locCols[1, ], 
                  stop = locCols[2, ])
  colnames(Values) = varNames
  
  return(Values)
}


selectCols = function(shortColNames, headerRow, searchLocs) {
  sapply(shortColNames, function(shortName, headerRow, searchLocs){
    startPos = regexpr(shortName, headerRow)[[1]]
    if (startPos == -1) return( c(NA, NA) )
    index = sum(startPos >= searchLocs)
    c(searchLocs[index] + 1, searchLocs[index + 1])
  }, headerRow = headerRow, searchLocs = searchLocs )
}

convertTime = function(time) {
  timePieces = strsplit(time, ":")
  timePieces = sapply(timePieces, as.numeric)
  sapply(timePieces, function(x) {
                      if (length(x) == 2) x[1] + x[2]/60
                      else 60*x[1] + x[2] + x[3]/60
                      })
}
createDF = function(Res, year, sex) 
{
  # Determine which time to use
  if ( !is.na(Res[1, 'net']) ) useTime = Res[ , 'net']
  else if ( !is.na(Res[1, 'gun']) ) useTime = Res[ , 'gun']
  else useTime = Res[ , 'time']
  
  # Remove # and * and blanks from time
  useTime = gsub("[#\\*[:blank:]]", "", useTime)
  runTime = convertTime(useTime[ useTime != "" ])
  
  # Drop rows with no time
  Res = Res[ useTime != "", ]
  
  Results = data.frame(year = rep(year, nrow(Res)),
                       sex = rep(sex, nrow(Res)),
                       name = Res[ , 'name'], home = Res[ , 'home'],
                       age = as.numeric(Res[, 'ag']), 
                       runTime = runTime,
                       stringsAsFactors = FALSE)
  invisible(Results)
}


```


```{r}

urlsV2[1]
```


```{r}
years = 1999:2012

###Correct function for 1999 normalization
#### Corrected function to pull down Male tables with consistent format
mensTables = lapply (urlsV2, extractResTableV2)

menTablesV2 = mapply(extractResTableV2, url = urlsV2, year = years)
names(menTablesV2) = years
sapply(menTablesV2, length)

#### Confirmation that the 1999 and other years have consistent formatting
#####menTablesV2$'1999'[1:10]
####menTablesV2[[2]][1:10]
menTablesV2[[3]][1:10]
#####menTablesV2[[4]][1:10]
#####menTablesV2[[5]][1:10]
#####menTablesV2[[6]][1:10]
#####menTablesV2[[7]][1:10]
menTablesV2[[8]][1:10]
#### Save the outputs
save(menTablesV2, file = "CBMenTextTables_Houssaye.rda")

```




```{r}


separatorIdx = grep("^===", menTablesV2[["2006"]])
separatorRow = menTablesV2[['2006']][separatorIdx]
separatorRowX = paste(substring(separatorRow, 1, 63), " ", 
                      substring(separatorRow, 65, nchar(separatorRow)), 
                      sep = "")
menTablesV2[['2006']][separatorIdx] = separatorRowX




```



```{r}



menResMat = lapply(menTablesV2, extractVariables)


## looking at results and it appears we have peeled out headers.  Now time to explore individual years

```

```{r}
menDF = mapply(createDF, menResMat, year = 1999:2012,
               sex = rep("M", 14), SIMPLIFY = FALSE)
sapply(menDF, nrow)
#remove records with NA for age
menDF$`1999` = menDF$`1999`[-which(is.na(menDF$`1999`$age)),]
menDF$`2002` = menDF$`2002`[-which(is.na(menDF$`2002`$age)),]
menDF$`2005` = menDF$`2005`[-which(is.na(menDF$`2005`$age)),]
menDF$`2007` = menDF$`2007`[-which(is.na(menDF$`2007`$age)),]
menDF$`2009` = menDF$`2009`[-which(is.na(menDF$`2009`$age)),]
menDF$`2010` = menDF$`2010`[-which(is.na(menDF$`2010`$age)),]
menDF$`2012` = menDF$`2012`[-which(is.na(menDF$`2012`$age)),]


sapply(menDF, nrow)
cbMen = do.call(rbind, menDF)



```
```{r Testcode}

# READ-WRITE CSV
cbMen_path <- "C:/Users/brndn/OneDrive/Documents/GitHub/Homework3/7333-Case-Study-Two/cbMen.csv"

read_or_write = "read"

if (read_or_write == 'read'){
  
  cbMen <- read_csv(cbMen_path, col_names = TRUE,
                    col_types = cols(year =
                                     col_double(),
                                     sex = col_character(),
                                     name = col_character(),
                                     home = col_character(),
                                     age = col_double(),
                                     runTime = col_double()
                                     )
                    )
  
} else if(read_cbMen == 'write'){
  
  write_csv(cbMen, cbMen_path)
  }



# RECORD COUNT: 70047
boxplot(runTime~year,data=cbMen, main="Cherry Blossom: Men's Run Time By Year", xlab="Year", ylab="Time (Minutes)") 

# DROP THE ERROR FROM THE DATASET
cbMen <- filter(cbMen, !(year==2001 & runTime == min(runTime) & age == 70))

# RECORD COUNT: 70046
# BOXPLOT: runTime by Year
image_location = "C:/Users/brndn/OneDrive/Documents/GitHub/Homework3/7333-Case-Study-Two/Images/Boxplot/"
par(mfrow=c(1,1))
jpeg(paste(image_location, "mens_runTime_by_Year.jpeg"))
boxplot(runTime~year,data=cbMen, main="Cherry Blossom: Men's Run Time By Year", xlab="Year", ylab="Time (Minutes)")
dev.off()

# BOXPLOT: AGE BY YEAR
boxplot(age~year,data=cbMen, main="Cherry Blossom: Men's Age by Year", xlab="Year", ylab="Runner's Age")


# LOCATE AND REMOVE AGE OUTLIERS
cbMen <- filter(cbMen, !(year %in% c(2001:2003) & age %in% c(0,1, 2, 4)))

# RECORD COUNT: 70039
# BOXPLOT: Age by Year
par(mfrow=c(1,1))
jpeg(paste(image_location, "mens_age_by_Year.jpeg"))
boxplot(age~year,data=cbMen, main="Cherry Blossom: Men's Age by Year", xlab="Year", ylab="Runner's Age")
dev.off()

image_location = "C:/Users/brndn/OneDrive/Documents/GitHub/Homework3/7333-Case-Study-Two/Images/QQ_Plot/"

# QQ PLOT: AGE
par(mfrow=c(1,1))
jpeg(paste(image_location, "mens_age_qq_plot.jpeg"))
qqnorm(cbMen$age, main = "Q-Q Plot: Men's Age")
qqline(cbMen$age)
dev.off()

# QQ PLOT: AGE BY YEAR
#par("mar")
#par(mar=c(1,1,1,1))
#jpeg(paste(image_location, "mens_age_by_year_qq_plot.jpeg"))
#par(mfrow=c(8,2))
#for (i in seq(from=1999, to=2012, by=1)){
#  temp <- filter(cbMen, year == i)

#  qqnorm(temp$age, main = paste("Q-Q Plot: Men's Age: ", i, sep=" "))
#  qqline(temp$age)
#}
#dev.off()

par(mar=c(1,1,1,1))

par(mfrow=c(1,1))
for (i in seq(from=1999, to=2012, by=1)){
  temp <- filter(cbMen, year == i)
  jpeg(paste(image_location, "mens_age_by_", i, "_qq_plot.jpeg"))
  qqnorm(temp$age, main = paste("Q-Q Plot: Men's Age: ", i, sep=" "))
  qqline(temp$age)
  Sys.sleep(1)
  dev.off()
}


# QQ PLOT: RUNTIME
par("mar")
par(mar=c(1,1,1,1))
par(mfrow=c(1,1))
jpeg(paste(image_location, "mens_runtime_qq_plot.jpeg"))
qqnorm(cbMen$runTime, main = "Q-Q Plot: Men's runTime")
qqline(cbMen$runTime)

# QQ PLOT: RUNTIME BY YEAR
par("mar")
par(mar=c(1,1,1,1))

par(mfrow=c(1,1))

for (i in seq(from=1999, to=2012, by=1)){
  temp <- filter(cbMen, year == i)
  jpeg(paste(image_location, "mens_runtime_by_", i, "_qq_plot.jpeg"))
  qqnorm(temp$runTime, main = paste("Q-Q Plot: Men's Runtime: ", i, sep=" "))
  qqline(temp$runTime)
  Sys.sleep(1)
  dev.off()
}

image_location = "C:/Users/brndn/OneDrive/Documents/GitHub/Homework3/7333-Case-Study-Two/Images/Density/"

# DENSITY CURVE - AGE
for (i in seq(from=1999, to=2012, by=1)){
  temp <- filter(cbMen, year == i)
  jpeg(paste(image_location, "mens_age_by_", i, "_density.jpeg"))
  hist(temp$age, mean(temp$age), prob=T, main =  paste("Density: Men's Age: ", i, sep=" "))
  lines(density(temp$age))
  Sys.sleep(1)
  dev.off()
}

# DENSITY CURVE - RUNTIME
for (i in seq(from=1999, to=2012, by=1)){
  temp <- filter(cbMen, year == i)
  jpeg(paste(image_location, "mens_runtime_by_", i, "_density.jpeg"))
  hist(temp$runTime, mean(temp$runTime), prob=T, main =  paste("Density: Men's runTime: ", i, sep=" "))
  lines(density(temp$runTime))
  Sys.sleep(1)
  dev.off()
}

dev.set(dev.next())
temp <- filter(cbMen, year == 1999)
hist(temp$age, 20, prob=T)
lines(density(temp$age))
```

```{r}
#URL for WOMEN and Library

library(XML)
ubase = "http://www.cherryblossom.org/"

#### Revised URLS
womenURLs = 
  c("results/1999/cb99f.html", #"cb99f.htm"
    "results/2000/Cb003f.htm", #"cb003f.htm"
    "results/2001/oof_f.html", #"results/2001/oof_f.html"
    "results/2002/ooff.htm", #"results/2002/ooff.htm"
    "results/2003/CB03-F.HTM", #"results/2003/CB03-F.HTM"
    "results/2004/women.htm", #"results/2004/women.htm"
    "results/2005/CB05-F.htm", #"results/2005/CB05-F.htm"
    "results/2006/women.htm", #"results/2006/women.htm"
    "results/2007/women.htm", #"results/2007/women.htm"
    "results/2008/women.htm", #"results/2008/women.htm"
    "results/2009/09cucb-F.htm", #"results/2009/09cucb-F.htm"
    "results/2010/2010cucb10m-f.htm", #"results/2010/2010cucb10m-f.htm"
    "results/2011/2011cucb10m-f.htm", #"results/2011/2011cucb10m-f.htm"
    "results/2012/2012cucb10m-f.htm" #"results/2012/2012cucb10m-f.htm"
    )
####


#### women URLS
urlsV3 = paste(ubase, womenURLs, sep="")
urlsV3[1:4]

urlsV3[1]

```

```{r}

womenTables = lapply(urlsV3, extractResTableV3)

#womenTables[[3]][1:3] = mensTables[[3]][1:3]
#womenTables[[3]] = append(x=womenTables[[3]], values=mensTables[[3]][4:5], after = 3)

years1 = 1999:2012



womenTablesv2 <- mapply(extractResTableV3, url = urlsV3, year = years1)
names(womenTablesv2) = years1
sapply(womenTablesv2, length)

###womenTablesv2[[1]][1:10]
###womenTablesv2[[2]][1:10]
###womenTablesv2[[3]][1:10]
###womenTablesv2[[4]][1:10]
###womenTablesv2[[5]][1:10]
###womenTablesv2[[6]][1:10]
###womenTablesv2[[7]][1:10]
###womenTablesv2[[8]][1:10]

save(womenTablesv2, file = "CBWoMenTextTables_Houssaye.rda")
```

```{r fix2001Women}
womenTablesv2[["2001"]][1:3] <- menTablesV2[["2001"]][1:3]
womenTablesv2[["2001"]] <- append(x=womenTablesv2[["2001"]], values=menTablesV2[["2001"]][4:5], after = 3)
```

```{r parseWomenData}
separatorIdxWomen = grep("^===", womenTablesv2[["2006"]])
separatorRowWomen = womenTablesv2[['2006']][separatorIdxWomen]
separatorRowXWomen = paste(substring(separatorRowWomen, 1, 63), " ", 
                      substring(separatorRowWomen, 65, nchar(separatorRowWomen)), 
                      sep = "")
womenTablesv2[['2006']][separatorIdxWomen] = separatorRowXWomen

womenResMat = sapply(womenTablesv2, extractVariables)
womenDF = mapply(createDF, womenResMat, year = 1999:2012,
               sex = rep("F", 14), SIMPLIFY = FALSE)
sapply(womenDF, nrow)
sapply(womenDF, nrow)
cbWomen = do.call(rbind, womenDF)
```
```{r removeWomenNA}
womenDF$`1999` = womenDF$`1999`[-which(is.na(womenDF$`1999`$age)),]
womenDF$`2002` = womenDF$`2002`[-which(is.na(womenDF$`2002`$age)),]
womenDF$`2005` = womenDF$`2005`[-which(is.na(womenDF$`2005`$age)),]
womenDF$`2006` = womenDF$`2006`[-which(is.na(womenDF$`2006`$age)),]
womenDF$`2007` = womenDF$`2007`[-which(is.na(womenDF$`2007`$age)),]
womenDF$`2009` = womenDF$`2009`[-which(is.na(womenDF$`2009`$age)),]
```

```{r writeWomenCSV}
# READ-WRITE CSV
cbWomen_path <- "../7333-Case-Study-Two/cbWomen.csv"

read_or_write = "read"

if (read_or_write == 'read'){
  
  cbWomen <- read_csv(cbWomen_path, col_names = TRUE,
                    col_types = cols(year =
                                     col_double(),
                                     sex = col_character(),
                                     name = col_character(),
                                     home = col_character(),
                                     age = col_double(),
                                     runTime = col_double()
                                     )
                    )
  
} else if(read_or_write == 'write'){
  
  write_csv(cbWomen, cbWomen_path)
  }
```

```{r}

#2001 table rows 1-10
##2001 Women's table has no "===" row and no variable names.  need to include those elements in for 2001.

library(dplyr)
library(tidyr)
#install.packages("splitstackshape")
library(splitstackshape)
library(stringr)
library(stringi)

varNamesv2 <- c("Place", "Num Name","Ag Hometown", "Net Gun")

####stri_length(womenTablesv2[[3]])
####womenTablesv2[[3]] <- womenTablesv2[[3]][3:2976]
####womenTablesv2[[3]][1:10]
####womenTablesv2[[3]] <- paste(womenTablesv2[[3]],varNamesv2,sep = " ")
####womenTablesv2[[3]][1:10]

Women03 = as.data.frame(womenTablesv2[[3]])
colnames(Women03) <- c("column")
women03v2 <- concat.split(Women03,"column","     ")
women03v3 <- women03v2[,-1]
women03v4 <- women03v3[-(1:3),]
colnames(women03v4) <- c("Place", "Num Name","Ag Hometown", "Net","Gun")
women03v4[1:10,]


```









##women03v3 <- as.data.frame(paste(women03v2[3],women03v2[4]))


col_women03 <- c("PLACE","NUM","AG","HOMETOWN","NET","GUN")



womenResMat = lapply(womenTablesv2, extractVariables)



```


woIndex = grep("^    ", womenTablesv2[["2001"]])
woIndex

wspacerrow <- womenTablesv2[["2001"]][woIndex]
wheaderrow <- womenTablesv2[["2001"]][woIndex]
varNames <- c("Place", "Div/Tot", "Num", "Name", "Ag", "Hometown", "Net Tim", "Gun Tim", "Pace", "S")
str_replace(wheaderrow,"     ",varNames)
womenTablesv2[["2001"]][1:10]

separatorIdx1 = grep("^===", womenTablesv2[["2001"]])
separatorRow1 = womenTablesv2[['2001']][separatorIdx]
separatorRowX1 = paste(substring(separatorIdx1, 1, 63), " ", sep = "") 

separatorIdx = grep("^===", menTablesV2[["2001"]])
separatorRow = menTablesV2[['2006']][separatorIdx]
separatorRowX = paste(substring(separatorRow, 1, 63), " ", 
                      substring(separatorRow, 65, nchar(separatorRow)), 
                      sep = "")
menTablesV2[['2006']][separatorIdx] = separatorRowX


Women03 <- as.data.frame(womenTablesv2[[3]])
colnames(Women03) <- c("column")
women03v2 <- concat.split(Women03,"column","     ")
women03v3 <- (women03v2[,-1:-3])
women03v4 <- paste[women033,4]

menTablesV2[[3]][1:10]
mens2003col <- menTablesV2[[3]][3:4,]
















##Disregard following code:  attacked it from first try to sepearte into DFs and then recombine.  easier to use function provided.

#1.  Seperate Years into individual DF.



m1999 = as.data.frame(menResMat[[1]])
m2000 = as.data.frame(menResMat[[2]])
m2001 = as.data.frame(menResMat[[3]])
m2002 = as.data.frame(menResMat[[4]])
m2003 = as.data.frame(menResMat[[5]])
m2004 = as.data.frame(menResMat[[6]])
m2005 = as.data.frame(menResMat[[7]])
m2006 = as.data.frame(menResMat[[8]])
m2007 = as.data.frame(menResMat[[9]])
m2008 = as.data.frame(menResMat[[10]])
m2009 = as.data.frame(menResMat[[11]])
m2010 = as.data.frame(menResMat[[12]])
m2011 = as.data.frame(menResMat[[13]])
m2012 = as.data.frame(menResMat[[14]])

#2.  Create new variable for year

m1999$newcolumn = 1999
m2000$newcolumn = 2000
m2001$newcolumn = 2001
m2002$newcolumn = 2002
m2003$newcolumn = 2003
m2004$newcolumn = 2004
m2005$newcolumn = 2005
m2006$newcolumn = 2006
m2007$newcolumn = 2007
m2008$newcolumn = 2008
m2009$newcolumn = 2009
m2010$newcolumn = 2010
m2011$newcolumn = 2011
m2012$newcolumn = 2012

## do not do this step unless you accidentally created an extra column for 1999 file

m1999 <- m1999[ -c(8)]

names(m1999)[7] <- "Year"
names(m2000)[7] <- "Year"
names(m2001)[7] <- "Year"
names(m2002)[7] <- "Year"
names(m2003)[7] <- "Year"
names(m2004)[7] <- "Year"
names(m2005)[7] <- "Year"
names(m2006)[7] <- "Year"
names(m2007)[7] <- "Year"
names(m2008)[7] <- "Year"
names(m2009)[7] <- "Year"
names(m2010)[7] <- "Year"
names(m2011)[7] <- "Year"
names(m2012)[7] <- "Year"


MENSDF <- rbind(m1999,m2000,m2001,m2002,m2003,m2004,m2005,m2006,m2007,m2008,m2009,m2010,m2011,m2012)
MENSDF <- as.numeric(MENSDF$ag)



boxplot(MENSDF$ag ~ MENSDF$Year, data = MENSDF)





