---
title: "Quantifying_casestudy4"
author: "Brandon"
date: "September 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#URL for MEN and Library

library(XML)
ubase = "http://www.cherryblossom.org/"

#### From text
menURLs = 
  c("cb99m.htm", 
    "cb003m.htm", 
    "results/2001/oof_m.html",
    "results/2002/oofm.htm", 
    "results/2003/CB03-M.HTM",
    "results/2004/men.htm", 
    "results/2005/CB05-M.htm", 
    "results/2006/men.htm", 
    "results/2007/men.htm", 
    "results/2008/men.htm", 
    "results/2009/09cucb-M.htm",
    "results/2010/2010cucb10m-m.htm", 
    "results/2011/2011cucb10m-m.htm",
    "results/2012/2012cucb10m-m.htm")
####

#### Revised URLS
menURLsV2 = 
  c("results/1999/cb99m.html", #"cb99m.htm"
    "results/2000/Cb003m.htm", #"cb003m.htm"
    "results/2001/oof_m.html", #"results/2001/oof_m.html"
    "results/2002/oofm.htm", #"results/2002/oofm.htm"
    "results/2003/CB03-M.HTM", #"results/2003/CB03-M.HTM"
    "results/2004/men.htm", #"results/2004/men.htm"
    "results/2005/CB05-M.htm", #"results/2005/CB05-M.htm"
    "results/2006/men.htm", #"results/2006/men.htm"
    "results/2007/men.htm", #"results/2007/men.htm"
    "results/2008/men.htm", #"results/2008/men.htm"
    "results/2009/09cucb-M.htm", #"results/2009/09cucb-M.htm"
    "results/2010/2010cucb10m-m.htm", #"results/2010/2010cucb10m-m.htm"
    "results/2011/2011cucb10m-m.htm", #"results/2011/2011cucb10m-m.htm"
    "results/2012/2012cucb10m-m.htm" #"results/2012/2012cucb10m-m.htm"
    )
####

#### Text URLS
urls = paste(ubase, menURLs, sep="")
urls[1:4]

#### Revised URLS
urlsV2 = paste(ubase, menURLsV2, sep="")
urlsV2[1:4]

```

```{r}

#FUNCTIONS

#extractResTablev2

extractResTableV2 =
  #
  # Retrieve data from web site, 
  # find the preformatted text,
  # and write lines or return as a character vector.
  #
  function(url = "http://www.cherryblossom.org/results/2009/09cucb-F.htm",
           year = 1999, sex = "male", file = NULL)
  {
    #added encoding for windows users who get an "A" symbol
    doc = htmlParse(url, encoding="UTF-8")
    
    if (year == 2000) {
      # Get preformatted text from 4th font element
      # The top file is ill formed so the <pre> search doesn't work.
      ff = getNodeSet(doc, "//font")
      txt = xmlValue(ff[[4]])
      els = strsplit(txt, "\r\n")[[1]]
    }
    else if (year == 2009 & sex == "male") { 
      # Get preformatted text from <div class="Section1"> element
      # Each line of results is in a <pre> element
      div1 = getNodeSet(doc, "//div[@class='Section1']")
      pres = getNodeSet(div1[[1]], "//pre")
      els = sapply(pres, xmlValue)
    }
    else if (year == 1999 & sex == "male") { # have to add this else if statement
      # Get preformatted text from <pre> elements
      pres = getNodeSet(doc, "//pre")
      txt = xmlValue(pres[[1]])
      els = strsplit(txt, "\n")[[1]]   
    } 
    else {
      # Get preformatted text from <pre> elements
      pres = getNodeSet(doc, "//pre")
      txt = xmlValue(pres[[1]])
      els = strsplit(txt, "\r\n")[[1]]   
    } 
    
    if (is.null(file)) return(els)
    # Write the lines as a text file.
    writeLines(els, con = file)
  }


extractResTableV3 =
  #
  # Retrieve data from web site, 
  # find the preformatted text,
  # and write lines or return as a character vector.
  #
  function(url = "http://www.cherryblossom.org/results/2009/09cucb-F.htm",
           year = 1999, sex = "female", file = NULL)
  {
    #added encoding for windows users who get an "A" symbol
    doc = htmlParse(url, encoding="UTF-8")
    
    if (year == 2000) {
      # Get preformatted text from 4th font element
      # The top file is ill formed so the <pre> search doesn't work.
      ff = getNodeSet(doc, "//font")
      txt = xmlValue(ff[[4]])
      els = strsplit(txt, "\r\n")[[1]]
    }
    else if (year == 2009 & sex == "female") {
      # Get preformatted text from <div class="Section1"> element
      # Each line of results is in a <pre> element
      div1 = getNodeSet(doc, "//div[@class='Section1']")
      pres = getNodeSet(div1[[1]], "//pre")
      els = sapply(pres, xmlValue)
    }
    else if (year == 1999 & sex == "female") { # have to add this else if statement
      # Get preformatted text from <pre> elements
      pres = getNodeSet(doc, "//pre")
      txt = xmlValue(pres[[1]])
      els = strsplit(txt, "\n")[[1]]   
    } 
    else {
      # Get preformatted text from <pre> elements
      pres = getNodeSet(doc, "//pre")
      txt = xmlValue(pres[[1]])
      els = strsplit(txt, "\r\n")[[1]]   
    } 
    
    if (is.null(file)) return(els)
    # Write the lines as a text file.
    writeLines(els, con = file)
  }


#findColLocs

findColLocs = function(spacerRow) {

  spaceLocs = gregexpr(" ", spacerRow)[[1]]
  rowLength = nchar(spacerRow)

  if (substring(spacerRow, rowLength, rowLength) != " ")
    return( c(0, spaceLocs, rowLength + 1))
  else return(c(0, spaceLocs))
}

selectCols = function(shortColNames, headerRow, searchLocs) {
  sapply(shortColNames, function(shortName, headerRow, searchLocs){
    startPos = regexpr(shortName, headerRow)[[1]]
    if (startPos == -1) return( c(NA, NA) )
    index = sum(startPos >= searchLocs)
    c(searchLocs[index] + 1, searchLocs[index + 1])
  }, headerRow = headerRow, searchLocs = searchLocs )
}


#extractVariables

extractVariables = 
function(file, varNames =c("name", "home", "ag", "gun",
                           "net", "time"))
{
  
  # Find the index of the row with =s
  eqIndex = grep("^===", file)
  # Extract the two key rows and the data 
  spacerRow = file[eqIndex] 
  headerRow = tolower(file[ eqIndex - 1 ])
  body = file[ -(1 : eqIndex) ]
       # Remove footnotes and blank rows
  footnotes = grep("^[[:blank:]]*(\\*|\\#)", body)
  if ( length(footnotes) > 0 ) body = body[ -footnotes ]
  blanks = grep("^[[:blank:]]*$", body)
  if (length(blanks) > 0 ) body = body[ -blanks ]
  
  
  # Obtain the starting and ending positions of variables   
  searchLocs = findColLocs(spacerRow)
  locCols = selectCols(varNames, headerRow, searchLocs)
  
  Values = mapply(substr, list(body), start = locCols[1, ], 
                  stop = locCols[2, ])
  colnames(Values) = varNames
  
  return(Values)
}


selectCols = function(shortColNames, headerRow, searchLocs) {
  sapply(shortColNames, function(shortName, headerRow, searchLocs){
    startPos = regexpr(shortName, headerRow)[[1]]
    if (startPos == -1) return( c(NA, NA) )
    index = sum(startPos >= searchLocs)
    c(searchLocs[index] + 1, searchLocs[index + 1])
  }, headerRow = headerRow, searchLocs = searchLocs )
}

convertTime = function(time) {
  timePieces = strsplit(time, ":")
  timePieces = sapply(timePieces, as.numeric)
  sapply(timePieces, function(x) {
                      if (length(x) == 2) x[1] + x[2]/60
                      else 60*x[1] + x[2] + x[3]/60
                      })
}
createDF = function(Res, year, sex) 
{
  # Determine which time to use
  if ( !is.na(Res[1, 'net']) ) useTime = Res[ , 'net']
  else if ( !is.na(Res[1, 'gun']) ) useTime = Res[ , 'gun']
  else useTime = Res[ , 'time']
  
  # Remove # and * and blanks from time
  useTime = gsub("[#\\*[:blank:]]", "", useTime)
  runTime = convertTime(useTime[ useTime != "" ])
  
  # Drop rows with no time
  Res = Res[ useTime != "", ]
  
  Results = data.frame(year = rep(year, nrow(Res)),
                       sex = rep(sex, nrow(Res)),
                       name = Res[ , 'name'], home = Res[ , 'home'],
                       age = as.numeric(Res[, 'ag']), 
                       runTime = runTime,
                       stringsAsFactors = FALSE)
  invisible(Results)
}


```


```{r}
urls[1]
urlsV2[1]
```


```{r}
###Correct function for 1999 normalization
#### Corrected function to pull down Male tables with consistent format
menTablesV2 = mapply(extractResTableV2, url = urlsV2, year = years)
names(menTablesV2) = years
sapply(menTablesV2, length)

#### Confirmation that the 1999 and other years have consistent formatting
#####menTablesV2$'1999'[1:10]
#####menTablesV2[[2]][1:10]
#####menTablesV2[[3]][1:10]
#####menTablesV2[[4]][1:10]
#####menTablesV2[[5]][1:10]
#####menTablesV2[[6]][1:10]
#####menTablesV2[[7]][1:10]
#####menTablesV2[[8]][1:10]
#### Save the outputs
save(menTablesV2, file = "CBMenTextTables_Houssaye.rda")

```




```{r}


separatorIdx = grep("^===", menTablesV2[["2006"]])
separatorRow = menTablesV2[['2006']][separatorIdx]
separatorRowX = paste(substring(separatorRow, 1, 63), " ", 
                      substring(separatorRow, 65, nchar(separatorRow)), 
                      sep = "")
menTablesV2[['2006']][separatorIdx] = separatorRowX

```



```{r}



menResMat = lapply(menTablesV2, extractVariables)


## looking at results and it appears we have peeled out headers.  Now time to explore individual years

```

```{r}
menDF1 = mapply(createDF, menResMat, year = 1999:2012,
               sex = rep("M", 14), SIMPLIFY = FALSE)

menDF2 <- as.data.frame(menDF1)

length(menDF1)

sapply(menDF1, nrow)

cbMen = do.call(rbind, menDF1)

boxplot(cbMen$ag ~ cbMen$Year, data = cbMen)


###########Placholder for removing NA code
```


```{r}
#URL for WOMEN and Library

library(XML)
ubase = "http://www.cherryblossom.org/"

#### Revised URLS
womenURLs = 
  c("results/1999/cb99f.html", #"cb99f.htm"
    "results/2000/Cb003f.htm", #"cb003f.htm"
    "results/2001/oof_f.html", #"results/2001/oof_f.html"
    "results/2002/ooff.htm", #"results/2002/ooff.htm"
    "results/2003/CB03-F.HTM", #"results/2003/CB03-F.HTM"
    "results/2004/women.htm", #"results/2004/women.htm"
    "results/2005/CB05-F.htm", #"results/2005/CB05-F.htm"
    "results/2006/women.htm", #"results/2006/women.htm"
    "results/2007/women.htm", #"results/2007/women.htm"
    "results/2008/women.htm", #"results/2008/women.htm"
    "results/2009/09cucb-F.htm", #"results/2009/09cucb-F.htm"
    "results/2010/2010cucb10m-f.htm", #"results/2010/2010cucb10m-f.htm"
    "results/2011/2011cucb10m-f.htm", #"results/2011/2011cucb10m-f.htm"
    "results/2012/2012cucb10m-f.htm" #"results/2012/2012cucb10m-f.htm"
    )
####


#### women URLS
urlsV3 = paste(ubase, womenURLs, sep="")
urlsV3[1:4]

urlsV3[1]

```

```{r}
womenTables = lapply(urlsV3, extractResTableV3)


options(error = recover)
womenTablesv2 = mapply(extractResTableV3, url = urlsV3, year = years)
names(womenTables) = years
sapply(womenTables, length)

womenTables[2]



```
























##Disregard following code:  attacked it from first try to sepearte into DFs and then recombine.  easier to use function provided.

#1.  Seperate Years into individual DF.



m1999 = as.data.frame(menResMat[[1]])
m2000 = as.data.frame(menResMat[[2]])
m2001 = as.data.frame(menResMat[[3]])
m2002 = as.data.frame(menResMat[[4]])
m2003 = as.data.frame(menResMat[[5]])
m2004 = as.data.frame(menResMat[[6]])
m2005 = as.data.frame(menResMat[[7]])
m2006 = as.data.frame(menResMat[[8]])
m2007 = as.data.frame(menResMat[[9]])
m2008 = as.data.frame(menResMat[[10]])
m2009 = as.data.frame(menResMat[[11]])
m2010 = as.data.frame(menResMat[[12]])
m2011 = as.data.frame(menResMat[[13]])
m2012 = as.data.frame(menResMat[[14]])

#2.  Create new variable for year

m1999$newcolumn = 1999
m2000$newcolumn = 2000
m2001$newcolumn = 2001
m2002$newcolumn = 2002
m2003$newcolumn = 2003
m2004$newcolumn = 2004
m2005$newcolumn = 2005
m2006$newcolumn = 2006
m2007$newcolumn = 2007
m2008$newcolumn = 2008
m2009$newcolumn = 2009
m2010$newcolumn = 2010
m2011$newcolumn = 2011
m2012$newcolumn = 2012

## do not do this step unless you accidentally created an extra column for 1999 file

m1999 <- m1999[ -c(8)]

names(m1999)[7] <- "Year"
names(m2000)[7] <- "Year"
names(m2001)[7] <- "Year"
names(m2002)[7] <- "Year"
names(m2003)[7] <- "Year"
names(m2004)[7] <- "Year"
names(m2005)[7] <- "Year"
names(m2006)[7] <- "Year"
names(m2007)[7] <- "Year"
names(m2008)[7] <- "Year"
names(m2009)[7] <- "Year"
names(m2010)[7] <- "Year"
names(m2011)[7] <- "Year"
names(m2012)[7] <- "Year"


MENSDF <- rbind(m1999,m2000,m2001,m2002,m2003,m2004,m2005,m2006,m2007,m2008,m2009,m2010,m2011,m2012)
MENSDF <- as.numeric(MENSDF$ag)



boxplot(MENSDF$ag ~ MENSDF$Year, data = MENSDF)





